Supporting Information : Effect of copula on extinction risk

### 2019-02-28 SuppMat.Rmd
editing

  #ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  #plot(ss$d, ss$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
  #     axes=FALSE, type="l", col="orange")
 # abline(h=0,lty="dotted",col="grey")
 # lines(ss$d, ss$pop_avg_acf_right, col="skyblue")

@@

pdf(paste(resloc,"ricker_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted") #rc=1

@@

pdf(paste(resloc,"hassell_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted")

@@

pdf(paste(resloc,"pennycuick_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")

@@

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted")

@@

abrewer_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
abrewer_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
pdf(paste(resloc,"abrewer_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025left,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted")

>>>>

  #ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  #plot(ss$d, ss$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
  #     axes=FALSE, type="l", col="orange")
 # abline(h=0,lty="dotted",col="darkgrey")
 # lines(ss$d, ss$pop_avg_acf_right, col="skyblue")

@@

pdf(paste(resloc,"ricker_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="darkgrey") #rc=1

@@

pdf(paste(resloc,"hassell_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"pennycuick_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted",col="darkgrey")

@@

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted",col="darkgrey")

@@

abrewer_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
abrewer_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
pdf(paste(resloc,"abrewer_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025left,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted",col="darkgrey")
